% !TEX root = ../../../under-spec-z.tex

\section{Introduction} % (fold)
\label{sec:introduction}

    \subsection{Formatting} % (fold)
    \label{ssub:formatting}

        This paper consists of translated sections from \cite{Toen:2005wxa} as well as the author's own writing.
        The general layout and order tries to follow that of the original paper as much as possible, including section numbering and naming.

        Longer sections of translated text will be boxed, left aligned, sans serif, and ended with a small black square ($\blacksquare$).
        At the start of such sections there will also be a reference to the location of the source text.
        Shorter `quotations' will simply be in italics and referenced afterwards.
        Theorems (and definitions) that have been translated will not be boxed off or in quotes, but there will be a reference to the original theorem (or definition) after the theorem (or definition) number.
        Hopefully it will be largely self-explanatory, but here are a few guidelines that the author has tried to adhere to:
        \begin{itemize}
            \item Usually they will be given as a section and a paragraph, e.g. (\S1\,\P2), where the paragraphs are counted by looking at indentations.
            \item Negative paragraph numbers indicate counting from the end of the section (as given), with the last paragraph being the -1st.
                For example, (\S2.1\,\P-2) would indicate the penultimate paragraph of section 2.1.
                (Luckily there are no subsubsections, so we don't have to worry about things getting any more complex.)
        \end{itemize}


        Sometimes a section that we wish to translate will contain some reference to a theorem or definition in the original paper, and this might have a different numbering in \emph{this} paper.
        Because of this, all such references (e.g. \emph{voir définition 2.12}) from the original will be suitably replaced with numbering relevant to \emph{this} paper (e.g. \emph{voir \elide (\cref{le:yoneda-lemma})}).

        If there are any references to a certain section or paragraph without specifying from which paper, then they are to \cite{Toen:2005wxa}.
        Similarly, if any lemma (or theorem) is stated without a proof then a proof can be found in the referenced lemma (or theorem) in \cite{Toen:2005wxa}.

        Finally, all footnotes, in translated sections or not, are by the author and \emph{not} from \cite{Toen:2005wxa}.


    \subsubsection{Conventions} % (fold)
    \label{ssub:conventions}

        We retain the following conventions from \cite{Toen:2005wxa}:
        \begin{translation}{1}{-2}
            All the monoids and monoidal categories considered will be unital and associative, and all modules over a monoid will be unital.
            We will ignore all set-theoretic problems to do with the choice of universe; the reader can consult \cite{Toen:2005er,Toen:2008wy} to find a method to resolve them.
        \end{translation}

        We also impose the following conventions ourselves, which are always assumed (unless otherwise stated):
        \begin{itemize}
            \item all algebras and rings are unital and associative;
            \item $k$ is an algebraically closed field;
            \item $0\in\nn$;
            \item for a ring $R$ we write $R^\times$ to mean the group of multiplicative units in $R$;
            \item $\GG_m=k^\times=k\setminus\{0\}$;
            \item for $n\in\nn\setminus\{0\}$ we write $\mu_n$ to mean the cyclic group of order $n$;
            \item given a category $\ccat$ we write $x\in\ccat$ to mean $x\in\mathrm{ob}(\ccat)$;
            \item `presheaf' means a $\Set$-valued presheaf.
        \end{itemize}
        We usually use `functor' to mean `covariant functor'.
        % It is not a strict convention, but we tend to think of functors as being covariant (and hence contravariant functors are functors from the opposite category).
        % This is not a universal view though, and some papers don't adopt this tendency, but the context should always make it clear how we are thinking about functors.

    % subsubsection conventions (end)


    \input{content/sections/introduction/overview(int).tex}

    \input{content/sections/introduction/background(int).tex}

% section introduction (end)
