\documentclass{beamer}

\usetheme[numbering=fraction,block=fill]{metropolis}

\usepackage{mathrsfs}

\title{Twisting cochains and twisted complexes}
\subtitle{Simplicial methods in complex-analytic geometry}
\author{Tim Hosgood}
\institute{Université d'Aix-Marseille\\\url{https://thosgood.github.io}}
\date{24/07/19}

\begin{document}
    \begin{frame}
        \titlepage
    \end{frame}

    \begin{frame}
        \frametitle{Plan}
        \tableofcontents
    \end{frame}


    \section{History}

        \begin{frame}\frametitle{First steps}
            \begin{itemize}
                \item Edgar H Brown. ``Twisted tensor products, I''. In: \emph{Annals of Mathematics} 69.1 (1959), pp.~223--246.
                \item John C Moore. ``Differential homological algebra''. In: \emph{Actes du Congres International des Mathématiciens} 1 (1970), pp.~335--339.
            \end{itemize}
        \end{frame}

        \begin{frame}\frametitle{Coherent sheaves}
            \begin{itemize}
                \item Domingo Toledo and Yue Lin L Tong. ``A parametrix for $\delta$ and Riemann-Roch in Čech theory''. In: \emph{Topology} 15.4 (1976), pp.~273--301.
                \item Domingo Toledo and Yue Lin L Tong. ``Duality and Intersection Theory in Complex Manifolds. I''. In: \emph{Mathematische Annalen} 237 (1978), pp.~41--77.
                \item Nigel R O'Brian, Domingo Toledo, and Yue Lin L Tong. ``The Trace Map and Characteristic Classes for Coherent Sheaves''. In: \emph{American Journal of Mathematics} 103.2 (1981), pp.~225--252.
            \end{itemize}
        \end{frame}

        \begin{frame}\frametitle{Triangulation and stability}
            \begin{itemize}
                \item A I Bondal and M M Kapranov. ``Enhanced Triangulated Categories''. In: \emph{Math. USSR Sbornik} 70.1 (1991), pp.~1--15.
                \item Giovanni Faonte. \emph{Simplicial nerve of an A-infinity category}. 2015. arXiv: 1312.2127 [math.AT].
            \end{itemize}
        \end{frame}


    \section{Twisting cochains (OTT)}

        \subsection{The bicomplex}

            \begin{frame}\frametitle{Nice spaces}
                \begin{definition}[Stein spaces]
                    A complex-analytic\footnote{analytic = $\mathcal{O}_Y$ is holomorphic functions, $Y$ has the $\mathbb{C}^n$-induced topology; algebraic = $\mathcal{O}_Y$ is algebraic functions, $Y$ has the Zariski topology.} manifold $Y$ is said to be \emph{Stein} if it is
                    \begin{enumerate}
                        \item \emph{holomorphically convex}; and
                        \item \emph{holomorphically separable}.
                    \end{enumerate}
                \end{definition}

                \pause

                \begin{block}{Motto}
                    Stein things are nice.
                \end{block}

                \pause

                Throughout, $X$ is a complex-analytic manifold with a nice\footnote{\emph{Locally finite}, \emph{Stein}, and \emph{trivialising} (for the bundles in question).} cover $\mathcal{U}=\{U_\alpha\}_{\alpha\in I}$.
            \end{frame}

            \begin{frame}\frametitle{Endomorphisms of bounded-graded modules}
                Let $V=\{V_\alpha^\bullet\}$ be a collection of \emph{bounded-graded $\mathcal{O}_{U_\alpha}$-modules}:
                \begin{equation*}
                    V_\alpha^\bullet = \bigoplus_{q\in\mathbb{N}}V_\alpha^q\quad\text{such that }V_\alpha^q\text{ is zero for all but finitely many }q.
                \end{equation*}

                \pause

                Think of a bounded chain complex of vector bundles, but without the information of a differential.

                \pause

                \begin{definition}[Endomorphisms]
                    The collection of \emph{degree-$q$ endomorphisms $\mathrm{End}^q(V)$ of $V$} is, over each $U_{\alpha_0\ldots\alpha_p}$, given by
                    \begin{equation*}
                        \mathrm{End}^q(V)|U_{\alpha_0\ldots\alpha_p} = \bigoplus_{i\in\mathbb{Z}}\mathrm{Hom}\big( V_{\alpha_p}^i|U_{\alpha_0\ldots\alpha_p}, V_{\alpha_0}^{i+q}|U_{\alpha_0\ldots\alpha_p} \big).
                    \end{equation*}
                \end{definition}

                \pause

                \begin{alertblock}{Warning}
                    The maps are from the $\alpha_p$ part to the $\alpha_0$ part.
                \end{alertblock}
            \end{frame}

            \begin{frame}\frametitle{The deleted Čech complex}
                \begin{definition}[Deleted Čech complex]
                    Define the chain complex $(\hat{\mathscr{C}}^\bullet(\mathcal{U},\mathrm{End}^\circ(V)),\hat{\delta})$ by
                    \begin{equation*}
                        \hat{\mathscr{C}}^p\big(\mathcal{U},\mathrm{End}^q(V)\big) = \bigoplus_{(\alpha_0,\ldots,\alpha_p)} \mathrm{End}^q(V)|U_{\alpha_0\ldots\alpha_p}
                    \end{equation*}
                    (where $\mathrm{End}^q(V)|U_{\alpha_0\ldots\alpha_p}=0$ if $U_{\alpha_0\ldots\alpha_p}=\varnothing$) with the \emph{\textbf{deleted} Čech differential}
                    \begin{gather*}
                        \hat{\delta} \colon \hat{\mathscr{C}}^p\big(\mathcal{U},\mathrm{End}^q(V)\big) \to \hat{\mathscr{C}}^{p+1}\big(\mathcal{U},\mathrm{End}^q(V)\big)\\
                        (\hat{\delta}c)_{\alpha_0\ldots\alpha_{p+1}} = \sum_{i=1}^p (-1)^i c_{\alpha_0\ldots\widehat{\alpha_i}\ldots\alpha_{p+1}}.
                    \end{gather*}
                \end{definition}
            \end{frame}

            \begin{frame}\frametitle{A notational note}
                We use $\hat{\mathscr{C}}$ and $\hat{\delta}$ for the \emph{deleted} Čech objects and $\check{\mathscr{C}}$ and $\check{\delta}$ for the `full' Čech objects.
            \end{frame}

            \begin{frame}\frametitle{Further structure}
                \begin{itemize}
                    \item If $V$ has a differential then this gives us a \emph{bicomplex}.
                    \pause
                    \item There is a natural multiplication structure given by composition:
                        \begin{equation*}
                            (c^{p,q}\cdot \tilde{c}^{\tilde{p},\tilde{q}})_{\alpha_0\ldots\alpha_{p+\tilde{p}}} = (-1)^{q\tilde{p}} c_{\alpha_0\ldots\alpha_p}^{p,q} \tilde{c}_{\alpha_p\ldots\alpha_{p+\tilde{p}}}^{\tilde{p},\tilde{q}}.
                        \end{equation*}
                    \pause
                    \item We could define the same complex for an arbitrary bounded graded vector bundle, i.e.
                    \begin{equation*}
                        \hat{\mathscr{C}}^p(\mathcal{U},V^q) = \bigoplus_{(\alpha_0,\ldots,\alpha_p)} V_{\alpha_0}^q
                    \end{equation*}
                    but where the deleted Čech differential only omits the \emph{first} index (but includes the $(p+1)$th).
                \end{itemize}
            \end{frame}

            \begin{frame}\frametitle{A brief interlude on bundles}
                A holomorphic vector bundle $E$ on $X$ is described exactly by its \emph{transition maps $g_{\alpha\beta}\in\mathrm{GL}(n,\mathbb{C})$}, which describe the change in trivialisation from over $U_\beta$ to over $U_\alpha$.

                \pause

                These transition maps satisfy two conditions:

                \pause
                
                \begin{enumerate}
                    \item $g_{\alpha\beta}g_{\beta\gamma}=g_{\alpha\beta}$ (the \emph{cocycle} condition); and
                    \pause
                    \item $g_{\alpha\alpha}=\mathrm{id}$ (the \emph{invertibility} condition).
                \end{enumerate}

                \pause

                Note that these are maps from $E|U_{\alpha_p}$ to $E|U_{\alpha_0}$ in the specific case where $p=1$.
            \end{frame}

            \begin{frame}\frametitle{Rewriting the cocycle condition}
                Thinking of $g_{\alpha\beta}$ as an element of $\hat{\mathscr{C}}^1(\mathcal{U},E)$, we see that
                \begin{gather*}
                    (\hat{\delta}g)_{\alpha\beta\gamma} = -g_{\alpha\gamma}\\
                    (g\cdot g)_{\alpha\beta\gamma} = g_{\alpha\beta}g_{\beta\gamma}.
                \end{gather*}

                \pause

                This means that we can rewrite the cocycle condition as
                \begin{equation*}
                    \hat{\delta}g + g\cdot g = 0,
                \end{equation*}
                which looks like the \emph{Maurer-Cartan equation} (an observation to which we will later return).
            \end{frame}

            \begin{frame}\frametitle{Twisting cochains}
                \begin{definition}[Twisting cochains]
                    A \emph{(holomorphic) twisting cochain over $V$} is a formal sum
                    \begin{equation*}
                        \mathrm{a} = \bigoplus_{k\in\mathbb{N}} \mathrm{a}^{k,1-k}
                    \end{equation*}
                    where $\mathrm{a}^{k,1-k}\in\hat{\mathscr{C}}^k(\mathcal{U},\mathrm{End}^{1-k}(V))$ such that
                    \begin{enumerate}
                        \item $\hat{\delta}\mathrm{a} + \mathrm{a}\cdot\mathrm{a} = 0$; and
                        \item $\mathrm{a}_{\alpha\alpha}^{1,0}=\mathrm{id}$.
                    \end{enumerate}
                \end{definition}

                \pause

                The invertibility condition ``should'' really be weakened by asking only that $\mathrm{a}_{\alpha\alpha}^{1,0}$ be \emph{homotopic} to the identity.
            \end{frame}

            \begin{frame}\frametitle{Twisting cochains (cont.)}
                \begin{alertblock}{Warning}
                    The multiplication is \textbf{not} simply component-wise: it is given by taking all possible combinations, i.e.
                    \begin{equation*}
                        (\mathrm{a}\cdot\mathrm{b})^{p,s} = \bigoplus_{\substack{q+q'=p\\t+t'=s}} \mathrm{a}^{q,t}\cdot\mathrm{b}^{q',t'}.
                    \end{equation*}
                \end{alertblock}

                \pause
                
                \begin{itemize}
                    \item It might be the case that all but finitely many of the $\mathrm{a}^{k,1-k}$ are zero, but \textbf{never} $\mathrm{a}^{1,0}$, since it has to be the identity on $\alpha\alpha$.
                    \pause
                    \item If $V$ has a differential then $\mathrm{a}$ is an element of total degree $1$.
                    \pause
                    \item We haven't said \emph{when} twisting cochains exist, but under pretty mild assumptions they always do (by an inductive construction).
                \end{itemize}
            \end{frame}

            \begin{frame}\frametitle{Unpacking the definition}
                \begin{description}
                    \item[($k=0$) $\rightsquigarrow$] $\mathrm{a}_{\alpha}^{0,1}\cdot\mathrm{a}_{\alpha}^{0,1}=0$, which tells us that $\mathrm{a}_{\alpha}^{0,1}$ is a \emph{differential on $V_\alpha^\bullet$}.
                    \pause
                    \item[($k=1$) $\rightsquigarrow$] $\mathrm{a}_{\alpha}^{0,1}\cdot\mathrm{a}_{\alpha\beta}^{1,0} = \mathrm{a}_{\alpha\beta}^{1,0}\cdot\mathrm{a}_{\beta}^{0,1}$, which tells us that we have a \emph{chain map of chain complexes}
                        \begin{equation*}
                            \mathrm{a}_{\alpha\beta}^{1,0} \colon \big(V_\beta^\bullet|U_{\alpha\beta},\mathrm{a}_\beta^{0,1}\big) \to \big(V_\alpha^\bullet|U_{\alpha\beta},\mathrm{a}_\alpha^{0,1}\big)
                        \end{equation*}
                    \vspace{-1.5em}
                    \pause
                    \item[($k=2$) $\rightsquigarrow$] $-\mathrm{a}_{\alpha\gamma}^{1,0} + \mathrm{a}_{\alpha\beta}^{1,0}\cdot\mathrm{a}_{\beta\gamma}^{1,0} = \mathrm{a}_{\alpha}^{0,1}\cdot\mathrm{a}_{\alpha\beta\gamma}^{2,-1} + \mathrm{a}_{\alpha\beta\gamma}^{2,-1}\cdot\mathrm{a}_{\gamma}^{0,1}$, which says that $\mathrm{a}_{\alpha\beta\gamma}^{2,-1}$ witnesses a \emph{chain homotopy} between $\mathrm{a}_{\alpha\gamma}^{1,0}$ and $\mathrm{a}_{\alpha\beta}^{1,0}\cdot\mathrm{a}_{\beta\gamma}^{1,0}$.
                        On $\alpha\beta\alpha$ and $\beta\alpha\beta$ this tells us that $\mathrm{a}_{\alpha\beta}^{1,0}$ and $\mathrm{a}_{\beta\alpha}^{1,0}$ are \emph{chain homotopic inverses}, i.e. \emph{quasi-isomorphism}.
                \end{description}
            \end{frame}

            \begin{frame}\frametitle{Unpacking the definition (cont.)}
                \begin{description}
                    \item[($k\geqslant3$) $\rightsquigarrow$] some sort of `higher homotopic gluings', whatever this might mean.
                \end{description}

                \pause

                This is one of the things that we want to formalise!

                \pause

                \begin{block}{Extra-curricular}
                    By taking (internal) homology we obtain something strict: a complex of \emph{coherent sheaves} $\mathrm{H}^\bullet(\mathrm{a})$.
                    This is because quasi-isomorphisms become strict isomorphisms in homology.

                    We can use this fact to construct twisting cochains that resolve coherent sheaves by taking \emph{local} resolutions by vector bundles.
                \end{block}
            \end{frame}

        \subsection{The total complex}

            \begin{frame}\frametitle{The total differential}
                \begin{lemma}
                    For any $\mathrm{a}\in\mathrm{Tot}^1\hat{\mathscr{C}}^\bullet(\mathcal{U},\mathrm{End}^\circ(V))$, the map
                    \begin{align*}
                        \mathrm{D}_\mathrm{a} \colon \mathrm{Tot}^r\hat{\mathscr{C}}^\bullet(\mathcal{U},V^\circ) &\to \mathrm{Tot}^{r+1}\hat{\mathscr{C}}^\bullet(\mathcal{U},V^\circ)\\
                        c &\mapsto \hat{\delta}c+c\cdot\mathrm{a}
                    \end{align*}
                    defines a differential (i.e. squares to zero) if and only if $\mathrm{a}$ is a twisting cochain.
                \end{lemma}
                \begin{proof}
                    (Tedious) definition chasing.
                \end{proof}
            \end{frame}

            \begin{frame}\frametitle{The total differential (cont.)}
                We can actually define twisting cochains in a different way using this lemma (but we won't do so today).

                \pause

                But this approach lets us think of a twisting cochain as a \emph{first-order perturbation of the deleted Čech differential}.
            \end{frame}

            \begin{frame}\frametitle{Examples}
                \begin{example}
                    Look at the most trivial example: let $V$ be an \emph{ungraded} vector bundle, and $\mathrm{a} = \mathrm{a}^{0,1}+\mathrm{a}^{1,0}$, where $\mathrm{a}_{\alpha}^{0,1} = \mathrm{id}_{V_\alpha}$, and the $\mathrm{a}^{1,0}$ are the transition maps.
                    Then
                    \begin{equation*}
                        (\mathrm{D}_\mathrm{a}c)_{\alpha_0\ldots\alpha_{p+1}} = \mathrm{a}_{\alpha_0\alpha_1}^{1,0}c_{\alpha_1\ldots\alpha_{p+1}} + \sum_{i=1}^{p+1}(-1)^i c_{\alpha_0\ldots\widehat{\alpha_i}\ldots\alpha_{p+1}}.
                    \end{equation*}

                    \pause

                    Note that we couldn't use the full Čech differential on $\hat{\mathscr{C}}^\bullet(\mathcal{U},V^\circ)$ because everything has to lie over $U_{\alpha_0}$, but this total differential solves that problem --- recall that $\mathrm{a}_{\alpha_0\alpha_1}^{1,0}$ is a (quasi-)isomorphism.

                    \pause

                    A spectral-sequence argument shows that, in fact, $\mathrm{D}_\mathrm{a}$ here really is `the same as' the full Čech differential.
                \end{example}
            \end{frame}

            \begin{frame}\frametitle{Examples (cont.)}
                \begin{example}
                    Now look at a slightly-less trivial example: let $V^\bullet$ consist of \emph{complexes} $(V_\alpha^\bullet,\mathrm{d}_\alpha)$ of vector bundles, and $\mathrm{a} = \mathrm{a}^{0,1}+\mathrm{a}^{1,0}$, where $\mathrm{a}_{\alpha}^{0,1} = \mathrm{d}_\alpha$, and the $\mathrm{a}^{1,0}$ are the transition maps.
                    Then
                    \begin{align*}
                        (\mathrm{D}_\mathrm{a}c)_{\alpha_0\ldots\alpha_{p+1}} &= (-1)^p\mathrm{a}_{\alpha_0}^{0,1}c_{\alpha_0\ldots\alpha_p} + \mathrm{a}_{\alpha_0\alpha_1}^{1,0}c_{\alpha_1\ldots\alpha_{p+1}}\\
                        &\qquad+\sum_{i=1}^{p+1}(-1)^i c_{\alpha_0\ldots\widehat{\alpha_i}\ldots\alpha_{p+1}}.
                    \end{align*}

                    \pause
                    
                    Identifying the second and third terms with the full Čech differential, as above, gives the usual total differential of the Čech bicomplex:
                    \begin{equation*}
                        \mathrm{D}_\mathrm{a} = \check{\delta} \pm \mathrm{d}_V.
                    \end{equation*}
                \end{example}
            \end{frame}

        \subsection{Why this emphasis on the first index?}

        \subsection{Maurer-Cartan}


    \section{Twisted complexes (BK)}
        
        \subsection{Pretriangulated vs. triangulated}
        
        \subsection{Generalisation of twisting cochains}
    

    \section{Other fun things}

        \subsection{The A-infinity Yoneda embedding}
        
        \subsection{The bar construction}
        
        \subsection{Simplicial nerve}

\end{document}
